Papers

### 2022-12-31 quarto/index.qmd
Revert "div"
This reverts commit 9c43e3a7a19f272910bafa2d1cec48086f5d78ff.
update

<img src="img/aston.jpg"  border="0" vspace="10" hspace="0" class="bio-photo"><br>
<img src="img/email.png" height="30" width="200" vspace="0" ><br>

<p align="left">
	<a href="https://twitter.com/astonzhangAZ" title="Twitter" target="_blank"><img src="./img/logo-twitter.svg" class="bio-icon"></a>
	<a href="https://github.com/astonzhang" title="GitHub" target="_blank"><img src="./img/logo-github.svg" class="bio-icon"></a>
</p>

@@

>>>>

---
about:
  id: az-heading
  template: trestles
  image: img/aston.jpg
  image-width: 200px
  image-shape: rounded
  links:
    - icon: twitter
      text: Twitter
      href: https://twitter.com/astonzhangAZ
    - icon: github
      text: GitHub
      href: https://github.com/astonzhang
    - icon: bi-envelope
      text: Email
      href: img/email.png
---

:::{#az-heading}

@@

:::
